%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: WITH MODIFICATIONS BY BEN FIFIELD, 
% THIS TEMPLATE NEEDS TO BE COMPILED WITH LuaLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Ben}{Fifield, PhD}{ \urlstyle{same}\url{https://www.benfifield.com} | \href{https://github.com/bfifield}{\faGithub} \ \  \href{https://www.linkedin.com/in/ben-fifield}{\faLinkedin} \\
3515 Wesbrook Mall, Apt 309,Vancouver, BC, V6T 1W5\\
\href{mailto:benfifield@gmail.com}{benfifield@gmail.com} | (203) 858-9407
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Princeton University}
\descript{PhD, Politics}
\location{Jan. 2019 | Princeton, NJ}
\sectionsep

\descript{MA, Politics}
\location{Oct. 2013 | Princeton, NJ}
\sectionsep

\subsection{Washington University}
\subsection{in St. Louis}
\descript{BA, Political Science}
\location{May 2010 |  St. Louis, MO}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Programming}
\location{Languages:}
	\quad R \textbullet{} C++ \textbullet{} bash \\
\location{Data Management:} 
	\quad SQL (Vertica, MySQL)\\
\location{Document Preparation:} 
	\quad \LaTeX \textbullet{} knitr \textbullet{} RMarkdown\\
\location{Version Control:} 
	\quad git\textbullet{} svn\\
\location{Data Visualization:} 
	\quad ggplot2\\
\location{Bayesian Computing:} 
	\quad JAGS\textbullet{} stan\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOFTWARE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software}
\href{https://github.com/kosukeimai/fastLink}{\texttt{fastLink:}} Fast Probabilistic Record Linkage \vspace{1mm}

\href{https://github.com/kosukeimai/redist}{\texttt{redist:}} Markov chain Monte Carlo Methods for Redistricting Simulation\vspace{1mm}

\href{https://github.com/bfifield/hettx}{\texttt{hettx:}} Detecting and Measuring Treatment Effect Variation
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOFTWARE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Manuscripts}
\href{https://imai.fas.harvard.edu/research/linkage.html}{Using a Probabilistic Model to Assist Merging of Large-scale Administrative Records} (with Ted Enamorado and Kosuke Imai). American Political Science Review, 2019.\\\vspace{2mm}

\href{https://imai.fas.harvard.edu/research/files/redist.pdf}{Automated Redistricting Simulation using Markov chain Monte Carlo} (with Kosuke Imai, Michael Higgins, and Alexander Tarr). Forthcoming, Journal of Computational and Graphical Statistics.\\\vspace{2mm}

%\href{https://imai.fas.harvard.edu/research/files/enumerate.pdf}{The Essential Role of Empirical Validation in
%Legislative Redistricting Simulation} (with Kosuke Imai, Jun Kawahara, and Chris Kenny). Working Paper.\sectionsep

%%%%%%%%%
%    	OTHER
%%%%%%%%%
\section{Work Status}
US Citizen\\
Canadian resident on work visa, renewable in July 2021

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

\runsubsection{Facebook}
\descript{| Research Scientist}
\location{Dec. 2018-present | Seattle, WA\\ Sept. 2017 - Nov. 2017 (Research Intern) | Menlo Park, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item[-] Designed and implemented large-scale survey experiments in the United States, India, and Brazil, and communicated findings to stakeholders
\item[-] Developed new statistical methods for efficiently analyzing survey experiments at scale, reducing uncertainty of experimental estimates by on average 8pp
\item[-] Designed and ran large-scale online experiments to benchmark new survey designs for modeling individual-level treatment effects
\end{tightemize}
\sectionsep

\runsubsection{Hillary for America}
\descript{| Senior Data Scientist}
\location{Sept. 2015 - Nov. 2016 | New York, NY}
\begin{tightemize}
\item[-] Team leader responsible for managing three data scientists
\item[-] Directed statistical modeling of persuasion effects from survey experiments
\item[-] Developed new forecasting models to predict the election outcome, and provided daily reports to campaign leadership
\item[-] Developed statistical models of voter turnout and candidate support to optimize primary and general election resource allocation
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH + TEACHING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research and Teaching}
\runsubsection{Department of Politics, Princeton University}\\
\descript{Graduate Researcher}
\location{Sept. 2011 – Aug. 2015; Dec. 2016 - Nov. 2018}
\begin{tightemize}
\item[-] Developed new Markov chain Monte Carlo algorithms to improve the study and analysis of congressional redistricting
\item[-] Lead developer and maintainer of the R package \texttt{redist}, published on the \href{http://cran.r-project.org/web/packages/redist/}{Comprehensive R Archive Network}
\item[-] Designed new probabilistic record linkage algorithms to improve data integration in the social sciences, and implemented algorithms in R package \texttt{fastLink} published on the \href{http://cran.r-project.org/web/packages/fastLink/}{Comprehensive R Archive Network}
\item[-] Published an improved vote validation for the 2016 American National Election Study using \texttt{fastLink}
\item[-] Conducted independent research using large data sets such as national voter files and federal personnel databases, and presented at academic conferences
\end{tightemize}
\sectionsep

\descript{Instructor and Teaching Assistant}
\location{Jan. 2013 - May 2015}
\begin{tightemize}
\item[-] Taught ``boot camp'' in the statistical programming language R for Princeton University graduate students
\item[-] Teaching Assistant for \textit{Quantitative Analysis II}, a graduate statistics course focusing on causal inference, linear regression, maximum likelihood, and statistical computing (30 students)
\item[-] Teaching Assistant for \textit{Policymaking in America}, an undergraduate course on American political institutions (60 students)
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OTHER EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Consulting Experience}
\runsubsection{Commonwealth of Pennsylvania}
\descript{| Consulting Expert}
\location{Jan. 2018 - Feb. 2018 | Harrisburg, PA}
\begin{tightemize}
\item[-] Applied new Markov chain Monte Carlo algorithms to assess whether proposed Pennsylvania redistricting plans were gerrymandered
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}